Equivalence Testing and the Second Generation P-Value

### 2018-08-24 manuscript.Rmd
Typo's and details

On the other hand, if the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1). Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure  \ref{fig:TOSTSGPV1}).

@@

As the observed mean in a one-sample *t*-test lies closer to the test value (in the plot below, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
```{r, include=FALSE}
m <- 146
mu <- 144.5
sd <- 500
n <- 1000000
low_eqbound = -2 
high_eqbound = 2 
alpha = 0.05

@@

As we move the observed mean closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data is not uniformly distributed. The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r round(tail1, digits = 3)`, `r round(tail2, digits = 3)`, `r round(tail3, digits = 3)`, and `r round(tail4, digits = 3)`. As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C And D (`r round(tail3-tail4, digits = 3)`). Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at *p* = 0.5. Note that where the SGPV reaches 1 or 0, *p*-values closely approximate 0 and 1, but never reach these values.
##When are the SGPV and Equivalence Test Unrelated?
There are 4 situations where *p*-values from TOST and SGPV are unrelated. The first two situations were discussed before and can be seen in Figure \ref{fig:TOSTSGPV1}. When the SGPV is either 0 or 1 *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025. Because *p*-values approach 0 or 1, but are never exactly 0 or 1, and the SGPV is exactly 0 or 1, the two statistics are completely unrelated within these ranges. The easiest way to see this is by plotting the SGPV against the *p*-value from the TOST procedure. The situations where the SPGV and *p*-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical straight lines at second generation *p*-values of 0 and 1.
```{r, include=FALSE}
step = 0.01

@@

The *p*-value from the TOST procedure and the SGPV are also unrelated when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range. For example, in the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds. This means the SGPV is not set to 0.5, but it is constant across a range of observed means.
```{r, include=FALSE}
m <- 0.2
n <- 10
sd <- 1
d.lo <- -0.4
d.hi <- 0.4

>>>>

On the other hand, when the observed mean is 140, the equivalence test is not significant (the observed mean is far outside the equivalence range of 143 to 147), *t*(`r tost_res2$TOST_df`) = `r round(tost_res2$TOST_t1, digits = 2)`, *p* = `r round(tost_res2$TOST_p1, digits =  4)` (or more accurately, *p* > .999 as *p*-values are bounded between 0 and 1). Because the 95% CI falls completely outside the equivalence bounds, the SGPV is `r SGPV2` (see Figure  \ref{fig:TOSTSGPV1}).

@@

As the observed mean in a one-sample *t*-test lies closer to the test value (in Figure 4, from situation A to D, the mean gets closer to the test value by 0.1) the difference in the overlap changes uniformly.
```{r, include=FALSE}
m <- 146
mu <- 144.5
sd <- 500
n <- 1000000
low_eqbound = -2 
high_eqbound = 2 
alpha = 0.05

@@

As we move the observed mean closer to the test value in steps of 0.1 across A to D the *p*-value calculated for normally distributed data is not uniformly distributed. The probability of observing data more extreme than the upper bound of 2 is (from A to D) `r round(tail1, digits = 3)`, `r round(tail2, digits = 3)`, `r round(tail3, digits = 3)`, and `r round(tail4, digits = 3)`. As we can see, the difference between A and B (`r round(tail1-tail2, digits = 3)`) is not the same as the difference between C and D (`r round(tail3-tail4, digits = 3)`). Indeed, the difference in *p*-values is the largest as you start at *p* = 0.5 (when the observed mean falls on the test value), which is why the line in Figure \ref{fig:TOSTSGPV1} is the steepest at *p* = 0.5. Note that where the SGPV reaches 1 or 0, *p*-values closely approximate 0 and 1, but never reach these values.

##When are the SGPV and Equivalence Test Unrelated?

There are 4 situations where *p*-values from TOST and SGPV are unrelated. The first two situations were discussed before and can be seen in Figure \ref{fig:TOSTSGPV1}. When the SGPV is either 0 or 1 *p*-values from the equivalence test fall between 0.975 and 1 or between 0 and 0.025. Because *p*-values approach 0 or 1, but are never exactly 0 or 1, and the SGPV is exactly 0 or 1, the two statistics are completely unrelated within these ranges. The easiest way to see this is by plotting the SGPV against the *p*-value from the TOST procedure. The situations where the SPGV and *p*-values from the TOST procedure are unrelated are indicated by the parts of the curve where there are vertical straight lines at second generation *p*-values of 0 and 1.
```{r, include=FALSE}
step = 0.01

@@

The *p*-value from the TOST procedure and the SGPV are also unrelated when the CI is wider than the equivalence range (so the precision is low) and overlaps with the upper and lower equivalence bound, but the CI is *not* twice as wide as the equivalence range. In the example below, we see that the CI is only 1.79 times as wide as the equivalence bounds, but the CI overlaps with the lower and upper equivalence bounds. This means the SGPV is not set to 0.5, but it is constant across a range of observed means.
```{r, include=FALSE}
m <- 0.2
n <- 10
sd <- 1
d.lo <- -0.4
d.hi <- 0.4
